---
format: 
  revealjs
auto-stretch: false
---

# Welcome Back!

## Homework

::: incremental
-   Hand in report & **one** solution only <br> (unless otherwise instructed)

-   Homework is practice! If doing or completeing a particular problem is not productive, **don't do it!**.

-   I expect that you will check your answers with the textbook when possible.

-   Questions are great! But know that I usually can't answer -- unless with a short comment. Bring them to office hours!
:::

## Check-Ins

-   One note card/sheet only - no class notes or textbook.

## AEP

-   Need BOTH correct (mostly) solutions AND clear, complete explanations!

-   Marked on EMRI scale

    -   E: exceeds expectations
    -   M: meets expectations
    -   R: needs revisions
    -   I: incomplete (may not resubmit)

-   E or M counts as *completed*

## AEP 3
Area of Quad?

Median: 72785 ft^2

```{r}
#| echo: FALSE
#| include: FALSE

library(tidyverse)
area <- read_csv("../quadarea/data/area.csv")

```


```{r}
#| echo: FALSE

area |>
  ggplot( aes(x = area)) +
  geom_histogram(bins=20, col="white")
```

## Mean
```{r}
area |>
  summarize(mean = mean(area, na.rm = TRUE), 
            median = median(area, na.rm = TRUE),
            stdev = sd(area, na.rm = TRUE))

```

